A Comparison of Different GANs for Generating Handwritten Digits on MNIST

### 2020-04-11 proposal.tex
Added basic implementation details to paper

\begin{figure}[h!]
    \centering
    \includegraphics[width=9cm]{gan-arch.jpg}
    \caption{Architecture of a GAN}
    \label{fig:jupyter_server}
\end{figure}

@@

@@

@@

@@

@@

Our data was downloaded from Yann LeCun's website \footnote{\url{http://yann.lecun.com/exdb/mnist/}}.

@@

In this experement we cut off each GAN after a specif amount of Epochs. We compared the results of the three GAN architectures at 5, 15 and 30 Epochs.

@@

In this experiment we compare how the GAN algorithms run at different levels of training data from the MNIST set. We compare the GANS using the full training set, half the training set, and an eighth of the dataset.

>>>>

\begin{figure}[h!]
    \centering
    \includegraphics[width=9cm]{gan-arch.jpg}
    \caption{Architecture of a GAN}
    \label{fig:gan}
\end{figure}

@@

We implemented each GAN variety using PyTorch. PyTorch is an open source machine learning framework. This framework was used due to its popularity in the field and ease of use\cite{pytorch}.

@@

Using boilerplate PyTorch code we implemented a basic GAN that uses a generator and discriminator using simple neural networks. We used a Binary Cross Entropy (BCE) Loss function for the adversarial algorithm \cite{generalDeepLearning}. 
The arching idea of a basic GAN can be observed in figure \ref{fig:gan}.

@@

The code to actually run the DCGAN is identical to the code required to run the regular GAN. The key difference is that we use different types of neural networks in both implementations. In the GAN we just used a normal neural network, but, in the DCGAN we used convolutional neural networks where the generator mirrored the discriminator.

@@

The WGAN implementation was nearly identical to the normal GAN implementation but, the loss function was changed to be the Wasserstein distance. The key benefit of this is that the loss functions that we are trying to optimize now correlatie to image quality.

@@

The data we used was downloaded from Yann LeCun's website \footnote{\url{http://yann.lecun.com/exdb/mnist/}}.

@@

In this experiment we cut off each GAN after a specif amount of Epochs. We compared the results of the three GAN architectures at 5, 15 and 30 Epochs.

@@

In this experiment we compare how the GAN algorithms run at different levels of training data from the MNIST set. We compare the GANS using the full training set, half the training set, and an eighth of the dataset. Each algorithm was given 25 epochs to run.
